### 2025-01-08 paper/icml25/first/figs/shac.tex
revised figs to avoid overlaps

        % Draw number
        \node[circle, fill=Orange,draw=Orange] (s\i) at (\sx, 0) {\color{white}$s_\i$};
        \node[circle, fill=RoyalBlue,draw=RoyalBlue] (a\i) at (\ax, -1.4) {\color{white}$a_\i$};
        \node[circle, fill=DarkOrchid,draw=DarkOrchid] (r\i) at (\ax, +1.4) {\color{white}$r_\i$};

@@

    % reward function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1,color=DarkOrchid] (a\i) -- (r\i);
        \draw[-latex,line width=1,color=DarkOrchid] (s\i) -- ($(s\i) + (.6,0)$) to[out=0,in=270]   ($(r\i) - (0,.8)$) -- (r\i);
        \draw[-latex,line width=1,color=DarkOrchid] (s\j) -- ($(s\j) - (.6,0)$) to[out=180,in=270] ($(r\i) - (0,.8)$) -- (r\i);
        \node[circle, fill=DarkOrchid,draw=white, inner sep=1.5pt] (tmp) at ($(r\i) - (0,.8)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{DarkOrchid}$\hat{R}$};
    }

    % policy function
    \foreach \i in {0, ..., \nodes} {
        \draw[-latex,line width=1,color=RoyalBlue] (s\i) -- ($(s\i) - (0,1.2)$) to[out=270,in=180] ($(a\i) - (.9,0)$) -- (a\i);
        \node[circle, fill=RoyalBlue,draw=white, inner sep=1.5pt] (tmp) at ($(s\i) - (0,1.2)$) {};
        \node at ($(tmp) - (.2,0)$) {\color{RoyalBlue}$\pi$};
    }

    % value function
    \foreach \i in {1, ..., \nnodes} {
        \node[circle, fill=BlueGreen,draw=BlueGreen] (v\i) at ($(s\i) + (0,1.4)$) {\color{white}$v_\i$};
        \draw[-latex,line width=1, color=BlueGreen] (s\i) --  (v\i);
        \node[circle, fill=BlueGreen,draw=white, inner sep=1.5pt] (tmp) at ($(s\i) + (0,.6)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{BlueGreen}$V_\theta$};
    }

    % transition function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1, color=orange] (s\i) -- (s\j) ;
        \draw[-latex,line width=1, color=orange] (a\i) -- ($(a\i) + (0,1.1)$) to[out=90,in=180] ($(s\j) - (.9,0)$) -- (s\j);
        \node[circle, fill=orange,draw=white, inner sep=1.5pt] (tmp) at ($(s\j) - (.8,0)$) {};
        \node at ($(tmp) - (0,.3)$) {\color{orange}$\hat{F}$};
    }

>>>>

        % Draw number
        \node[circle, fill=Orange,draw=Orange] (s\i) at (\sx, 0) {\color{white}$s_\i$};
        \node[circle, fill=RoyalBlue,draw=RoyalBlue] (a\i) at (\ax, -1.4) {\color{white}$a_\i$};
        \node[circle, fill=DarkOrchid,draw=DarkOrchid] (r\i) at (\ax, +3.4) {\color{white}$r_\i$};

@@

    % reward function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1,color=DarkOrchid] (a\i) -- (r\i);
        \draw[-latex,line width=1,color=DarkOrchid,rounded corners=1ex] (s\i) -- ($(s\i) + (+.5,.6)$) -- ($(a\i) + (0,2)$) -- (r\i);
        \draw[-latex,line width=1,color=DarkOrchid,rounded corners=1ex] (s\j) -- ($(s\j) + (-.5,.6)$) -- ($(a\i) + (0,2)$) -- (r\i);
        \node[circle, fill=DarkOrchid,draw=white, inner sep=1.5pt] (tmp) at ($(r\i) - (0,.8)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{DarkOrchid}$\hat{R}$};
    }

    % policy function
    \foreach \i in {0, ..., \nodes} {
        \draw[-latex,line width=1,color=RoyalBlue] (s\i) -- ($(s\i) - (0,1.2)$) to[out=270,in=180] ($(a\i) - (.9,0)$) -- (a\i);
        \node[circle, fill=RoyalBlue,draw=white, inner sep=1.5pt] (tmp) at ($(s\i) - (0,1.2)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{RoyalBlue}$\pi_\theta$};
    }

    % value function
    \foreach \i in {1, ..., \nnodes} {
        \node[circle, fill=BlueGreen,draw=BlueGreen] (v\i) at ($(s\i) + (0,3.4)$) {\color{white}$v_\i$};
        \draw[-latex,line width=1, color=BlueGreen] (s\i) --  (v\i);
        \node[circle, fill=BlueGreen,draw=white, inner sep=1.5pt] (tmp) at ($(s\i) + (0,.6)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{BlueGreen}$V_\theta$};
    }

    % transition function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1, color=orange] (s\i) -- (s\j) ;
        \draw[-, line width=1, color=orange, rounded corners=1ex] (a\i) -- ($(a\i) + (.2,.5)$) -- ($(s\j) - (.8,0)$); 
        \node[circle, fill=orange,draw=white, inner sep=1.5pt] (tmp) at ($(s\j) - (.8,0)$) {};
        \node at ($(tmp) + (.1,.3)$) {\color{orange}$\hat{F}$};
    }

### 2025-01-08 paper/icml25/first/figs/shacpp.tex
revised figs to avoid overlaps

    % reward function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-,line width=1,color=DarkOrchid] (a\i) -- (R\i);
        \draw[-,line width=1,color=DarkOrchid] (sa\i) -- ($(sa\i) + (.6,0)$) to[out=0,in=270]   ($(R\i) - (0,.2)$) -- (R\i);
        \draw[-,line width=1,color=DarkOrchid] (sa\j) -- ($(sa\j) - (.6,0)$) to[out=180,in=270] ($(R\i) - (0,.2)$) -- (R\i);
    }

    % policy function
    \foreach \i in {0, ..., \nodes} {
        \draw[-latex,line width=1,color=RoyalBlue] (s\i) -- ($(s\i) - (0,1.2)$) to[out=270,in=180] ($(a\i) - (.9,0)$) -- (a\i);
        \node[circle, fill=RoyalBlue,draw=white, inner sep=1.5pt] (tmp) at ($(s\i) - (0,1.2)$) {};
        \node at ($(tmp) - (.2,0)$) {\color{RoyalBlue}$\pi$};
    }

@@

    % transition function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1, color=orange, dashed] (s\i) -- (s\j) ;
        \draw[-latex,line width=1, color=orange, dashed] (a\i) -- ($(a\i) + (0,1.1)$) to[out=90,in=180] ($(s\j) - (.9,0)$) -- (s\j);
        \node[circle, fill=orange,draw=white, inner sep=1.5pt] (tmp) at ($(s\j) - (.8,0)$) {};
        \node at ($(tmp) - (0,.3)$) {\color{orange}$\hat{F}$};
    }

>>>>

    % reward function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-,line width=1,color=DarkOrchid, rounded corners=1ex] (a\i) -- ($(a\i) + (-.2,.5)$) -- ($(R\i) - (.2,1.25)$) -- ($(R\i) - (0,1)$) -- (R\i);
        \draw[-,line width=1,color=DarkOrchid, rounded corners=1ex] (sa\i) -- ($(sa\i) + (.6,0)$) -- ($(R\i) - (0,.7)$) -- ($(R\i) - (0,.2)$) -- (R\i);
        \draw[-,line width=1,color=DarkOrchid, rounded corners=1ex] (sa\j) -- ($(sa\j) - (.6,0)$) -- ($(R\i) - (0,.7)$) -- ($(R\i) - (0,.2)$) -- (R\i);
    }

    % policy function
    \foreach \i in {0, ..., \nodes} {
        \draw[-latex,line width=1,color=RoyalBlue] (s\i) -- ($(s\i) - (0,1.2)$) to[out=270,in=180] ($(a\i) - (.9,0)$) -- (a\i);
        \node[circle, fill=RoyalBlue,draw=white, inner sep=1.5pt] (tmp) at ($(s\i) - (0,1.2)$) {};
        \node at ($(tmp) - (.25,0)$) {\color{RoyalBlue}$\pi_\theta$};
    }

@@

    % transition function
    \foreach \i in {0, ..., \nodes} {
        \pgfmathtruncatemacro{\j}{\i+1}
        \draw[-latex,line width=1, color=orange, dashed] (s\i) -- (s\j) ;
        \draw[-, line width=1, color=orange, dashed] (a\i) -- ($(a\i) + (.2,.5)$) -- ($(s\j) - (.8,0)$); 
        \node[circle, fill=orange,draw=white, inner sep=1.5pt] (tmp) at ($(s\j) - (.8,0)$) {};
        \node at ($(tmp) + (0,.3)$) {\color{orange}$\hat{F}$};
    }
